---
title: 'Homework #1 CSCI 036'
author: "Aditi Madhok"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<span style="color:blue">
**Statistics**
</span>

Find by hand the sample average of $3.1,4.2,$ and $2.6$. We can also do this in R by assigning the vector to a variable name, and then using the `mean` command.  Try the following code and see if your answer was correct:

```{r}
v <- c(3.1,4.2,2.6)
mean(v)
```

1.  The following command in R assigns a vector of length 4 to the variable `x`:

```{r echo=FALSE}
x <- c(0.3,0.1,0.4,0.7)
```
    (a) Find the sample average of the vector `x` with the `mean` command.

```{r echo=FALSE}
x <- c(0.3,0.1,0.4,0.7)
avg <- mean(x)
avg 
```

    
    (b) Find the sample standard deviation with the `sd` command.

```{r}
std <- sd(x)
std 
```

    (c) Use `sum` to add the values in the vector together.
    
```{r}
sum<- sum(x)
sum 
```
    
    (d) Find the sum of the squares of the values `x`. (Hint: Use `x^2` to get the vector whose components are the square of the entries in `x`.)
    
```{r}
sum_squares <- sum (x^2)
sum_squares
```
    

2. Consider the built in data set `ToothGrowth` in R.  

  a. What are the units on the dose of Vitamin C?  (Remember that you can information about a command or variable in R by typing a ? followed by the thing you are trying to get help about in the console.)

```{r}
units <- "milligrams"
```

    b. Use the `summary` command in the console to determine the mean length that the teeth grow in the guinea pigs.
    
```{r}
mean_length <- 18.81
```
   
    c. Use the `summary` command to find the median length that the teeth grow in the guinea pigs.
    
```{r}
median_length <- 19.25
```
   
    d. Use `plot(ToothGrowth$dose,ToothGrowth$len)` to see how the length of the teeth varies with Vitamin C dose.  From this plot, would you say that increased Vitamin C results in greater tooth length?

```{r}
answer <- "YES"
```


3.  The command
```
y <- runif(n = 10,min = 0, max = 1)
```
will generate 10 uniform random numbers from 0 to 1, and place them in the vector y.

    (a) Modify this command to create a vector z of a million uniforms. 
    
```{r}
z <- runif(n = 1000000,min = 0, max = 1)
```
    
    (b) Find the sample mean of your uniforms.
    
```{r}
z_mean <- mean(z)
z_mean
```

    
    (c) Find the sample standard deviation of your uniforms.

```{r}
z_std <- sd(z)
z_std
```

4. a. Write code to create a vector `u` consisting of the numbers 1, 2, 3 and 4. Then, create a vector called `a` which is 6*u. (Make sure you look at `a` to see what it is.)
  
```{r}
u <- 1:4
a <- 6*u
a
```

    b. Assign `w <- c(4,0,2,1)`.  Then, create a vector `b` which is `u*w`. (What vector is this?)
  
```{r}
w <- c(4,0,2,1)
b <- u*w
b
```

    c. Assign `x <- c(1,2)`.  Then, create a vector `c` which is `u*x`. (What is that?!)
    
```{r}
x <- c(1,2)
c <- u*x
c
```


