---
title: 'Homework #2:  Transforming Data'
author: "Aditi Madhok"
date: "2/3/21"
output:
  pdf_document: default
  html_document: default
---

Let's add our libraries first:
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(nycflights13)
```


1. Consider the `flights` variable from the `nycflights13` package.  Use the `select` command to create tibbles with the variables described below:

  a. Only the carrier and tail number.
  
```{r}
planes<- select(flights, carrier | tailnum)
planes
```

  b. All variables except the year.
  
```{r}
not_year<- select (flights, !(year))
not_year
```

  c. Any variable ending with the word `time'.
```{r}
time_variables<- select (flights, ends_with("time"))
time_variables
```

  d. The first 9 variables.
```{r}
first_nine<- select(flights, year : arr_delay)
first_nine
```


2. Use the filter function to find all the flights that satisfy the following conditions.

    a. Had an arrival delay of two or more hours.
    
```{r}
arr_delay_ge2 <- filter(flights, arr_delay>=120)
arr_delay_ge2
```
    
    b. Flew to Houston (airport codes `IAH` or `HOU`).

```{r}
to_houston <- filter(flights,dest =="IAH" | dest == "HOU")
to_houston
```

    
    c.  Departed from JFK in July.

```{r}
JFK_July<-filter(flights,origin =="JFK", month == "7")
JFK_July
```

   d. Another useful dplyr filtering helper is `between`.  Look up what it does and how to use it. Then, use it to find flights that left between 0 and 60 minutes late.

```{r}
late <- filter(flights, (between(dep_delay,0,60)))
late
```

  e. Filter the 'flights' dataset to *remove* all flights with missing departure times.
```{r}
flights_with_dep_time<-filter(flights,!is.na(dep_time))
flights_with_dep_time
```

----


3. Practice with mutate.

 a.  Consider the `distance` variable in the `flights` dataset.  Currently this is measured in miles.  Convert this to feet with the `mutate` command (the convereted variable should still be called 'distance').

```{r}
flights_with_feet <- mutate(flights, distance=distance*5280)
flights_with_feet
```


  b. Add a variable `speed` to the `flights` table that gives the average flight speed, **in miles per hour**.
  
```{r}
flights_with_speed<- mutate(flights,speed=distance/(air_time/60)) 
flights_with_speed
```

c. Add a variable to `flights` called `early` which is TRUE if the flight arrival early and FALSE if it arrived on time or late.

```{r}
early_flights<- mutate(flights,early=(arr_delay<0)) 
early_flights
```
  


----


4.  The `arrange` function sorts a variable from low to high. 

  a. Sort 'flights' so that the flights that departed closest to their scheduled departure time are first. 

```{r}
most_on_time<-arrange(flights, abs(dep_delay))
most_on_time
```

  b. Sort `flights` according to their arrival delay, **from high to low**.
  
```{r}
latest_arrival<- arrange(flights,desc(arr_delay))
latest_arrival
```


  
  c. Use `arrange` to sort `early_flights` (from Problem 3c) on the variable `early`.  (Is `TRUE` or `FALSE` the lower value?)
 #false is lower value so
```{r}
sorted_by_boolean<-arrange(early_flights)
sorted_by_boolean
```


----


