---
title: "Lab1"
author: "Aditi Madhok"
date: "1/26/2021"
output:
  pdf_document: default
  html_document:
    css: lab-style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tutorial Answers 

The *following* are **answers** to the lab.

# Section 1 

@. 
2:50
seq(50, 2, by=-2)

@.
z <- 8 
w <- 7 
z*w

@.
x <- c(-1,2,3)
x^(1/2)

# Section 2 

```{r cars, echo=TRUE}
summary(cars)
```


4. 
```{r,  echo=TRUE, fig.height = 8, fig.width = 8}
plot(pressure)
```

5.
```{r}
x <- 5
x^(1/2)
```


Here is my inline name $admadz$.
\[
ad + madz.
\]

$ad \geq madz$
*I am my family (name) but also my own **individual***

i am
$\bar{me}$

\[
\sum_{i = 0}^\infty \rho^i = \frac{1}{1 - \rho}.
\]

but make it LaTeX now (behind the scenes)

\[
\int_{i = 0}^1 x^2 \ dx = \frac{1}{3}.
\]

6. 
\[
sin (x)
\]

7. lol reference above 

8. $\pi$

9. 
```{r}
x <-13
x^(1/2)
```

11.
:::: {.theorem}
If $a$ and $b$ are the two shorter lengths of a right triangle, and $c$ is the longer length, th
en $a^2 + b^2 = c^2$.
::::
